If you\textquotesingle{}ve clicked on the \char`\"{}guidelines for contributing\char`\"{} link from the Git\+Hub issue tracker, you\textquotesingle{}re in the right place. These guidelines will help the development team fix the issue.

These links will pre-\/populate an issue with a template\+:

\begin{TabularC}{3}
\hline
\rowcolor{lightgray}{\bf Libraries }&{\bf Interfaces }&{\bf Other  }\\\cline{1-3}
\href{https://github.com/stan-dev/math/issues/new?body=%23%23%20Bug%20Report%0A%0A__Version__%0A%0A__Description__%0A%0A__Steps__%0A%0A__Output__%0A%0A__Expected%20Output__%0A%0A__Additional%20Information__%0A%0A}{\tt Math (bug report)} ~\newline
 \href{https://github.com/stan-dev/math/issues/new?body=%23%23%20Feature%20Request%0A%0A__Version__%0A%0A__Description__%0A%0A__Example__%0A%0A__Additional%20Information__%0A%0A}{\tt Math (feature request)} ~\newline
 &\href{https://github.com/stan-dev/cmdstan/issues/new?body=__CmdStan%20Version__%0A%0A__Operating%20System__%0A%0A__Compiler__%0A%0A__Description__%0A%0A__Steps__%0A%0A__Output__%0A%0A__Expected%20Output__%0A%0A__Additional%20Information__}{\tt Cmd\+Stan} ~\newline
 \href{https://github.com/stan-dev/rstan/issues/new?body=__RStan%20Version__%0A%0A__R%20version__%0A%0A__Operating%20System__%0A%0A__Compiler__%0A%0A__Description__%0A%0A__Steps__%0A%0A__Output__%0A%0A__Expected%20Output__%0A%0A__Additional%20Information__%0A}{\tt R\+Stan} ~\newline
 \href{https://github.com/stan-dev/pystan/issues/new?body=__PyStan%20Version__%0A%0A__Python%20version__%0A%0A__Operating%20System__%0A%0A__Compiler__%0A%0A__Description__%0A%0A__Steps__%0A%0A__Output__%0A%0A__Expected%20Output__%0A%0A__Additional%20Information__%0A}{\tt Py\+Stan} &\href{https://github.com/stan-dev/shinystan/issues/new?body=__shinyStan%20Version__%0A%0A__R%20version__%0A%0A__Operating%20System__%0A%0A__Description__%0A%0A__Steps__%0A%0A__Output__%0A%0A__Expected%20Output__%0A%0A__Additional%20Information__%0A}{\tt shiny\+Stan} \\\cline{1-3}
\href{https://github.com/stan-dev/stan/issues/new?body=%23%23%20Bug%20Report%0A%0A__Version__%0A%0A__Description__%0A%0A__Steps__%0A%0A__Output__%0A%0A__Expected%20Output__%0A%0A__Additional%20Information__%0A%0A}{\tt Stan (bug report)} ~\newline
 \href{https://github.com/stan-dev/stan/issues/new?body=%23%23%20Feature%20Request%0A%0A__Version__%0A%0A__Category__%0A%0A__Description__%0A%0A__Example__%0A%0A__Additional%20Information__%0A%0A}{\tt Stan (feature request)} &~\newline
 &~\newline
 \\\cline{1-3}
\end{TabularC}


\section*{Detailed information}

\subsection*{Math (bug report)}

Use this template for describing problems with the Stan Math Library. Please be as specific as possible. If you\textquotesingle{}re able to provide a simple reproducible example, this will go a long way to helping the developers fix the bug.

{\bfseries Title}

Please give a descriptive summary of the bug.

{\bfseries Version}

For tagged versions, please report the version number in {\ttfamily stan/math/version.\+hpp}.

For git cloned versions, report the result of typing {\ttfamily git rev-\/parse H\+E\+A\+D} from the command line.

{\bfseries Description}

Describe the problem as clearly as possible.

{\bfseries Steps}

Steps to reproduce the bug, if possible. If not, a description of how you discovered the bug.

If you have a reproducible example, put it here.

{\bfseries Output}

Output you get from triggering the bug. Knowing what Stan currently does is useful.

{\bfseries Expected Output}

Describe what you expected to happen. Knowing what the correct behavior should be is also very useful.

{\bfseries Additional Information}

Provide any additional information here.

\subsection*{Math (feature request)}

Use this template for requesting new features in Stan.

{\bfseries Title}

Please give a descriptive summary of the feature.

{\bfseries Version}

For tagged versions, please report the version number in {\ttfamily src/stan/version.\+hpp}.

For git cloned versions, report the result of typing {\ttfamily git rev-\/parse H\+E\+A\+D} from the command line.

{\bfseries Description}

Describe the feature you\textquotesingle{}d like in Stan. Be descriptive.

{\bfseries Example}

Provide at least one example. Also mock up the expected result from that example.

{\bfseries Additional Information}

Provide any additional information here. 